Simulation Study: Varying Effect Size

### 2018-08-06 datasets/simulations/simulations-varyingeffectsize.Rmd

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_cubic(0.90)              # numeric: proportion of null hypotheses
ts_dist <- rnorm_perturber(1/2)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1/2)    # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

>>>>

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_cubic(0.90)              # numeric: proportion of null hypotheses
ts_dist <- rnorm_perturber(1)       # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)      # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```
